\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-6pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-1pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-8pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-8pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\begin{center}
    \textbf{\Huge \scshape Pradyumna Kumar Sahoo} \\ \vspace{1pt}
    {\underline{pradyumna.sahoo@outlook.in}} $|$
    \small {\underline{+91-7540885886}} $|$
    \href{https://www.linkedin.com/in/prady029}{\underline{linkedin.com/in/prady029}} $|$
    \href{https://github.com/Prady029}{\underline{github.com/Prady029}} $|$
    \small {\underline{Hyderabad, India}}
\end{center}

%-----------SUMMARY-----------
\section{Summary}
\noindent\begin{minipage}{\linewidth}
Impact-driven Data Scientist with 5 years of experience building production-grade AI/ML systems across Medical AI, NLP, Computer Vision, and Generative AI. Proven track record in architecting GraphRAG pipelines, fine-tuning large medical language models, developing voice agents for clinical applications, and leading cross-functional teams. Seeking a Senior Data Scientist role to drive AI innovation at scale.
\end{minipage}

%-----------EXPERIENCE-----------
\section{Experience}

\resumeSubHeadingListStart
    \resumeSubheading
      {Data Scientist}{August 2025 -- Present}
      {Mondee Pvt. Ltd.}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Architected a \textbf{medical-grade GraphRAG chatbot} for clinical decision support by constructing structured knowledge graphs from medical textbooks using \textit{Neo4j} and \textit{AWS Neptune}, enabling doctors to query drug interactions and treatment protocols with traceable, hallucination-resistant responses via a \textit{LangChain}-powered retrieval layer.}
        \resumeItem{Engineered a \textbf{drug--drug interaction checker and dosage scheduler} served through a \textit{FastAPI} interface, integrating real-time data from \textbf{RxNorm} and \textbf{PubMed} APIs to surface conflict alerts and patient-specific dosage recommendations within the chat session.}
        \resumeItem{Led \textbf{end-to-end fine-tuning of Medgemma-27b-text-it} for domain-specific clinical NLP using \textit{PEFT / LoRA} with \textit{HuggingFace Transformers} and \textit{DeepSpeed}, coordinating data curation, training, and evaluation pipelines with engineers from \textbf{IIT Madras and IIT Hyderabad}.}
        \resumeItem{Directed \textbf{large-scale ASR data preparation and fine-tuning of gemma-3n-e2b-it} via \textit{QLoRA} and \textit{TGI}-based serving, overseeing audio collection, annotation, and quality control to build a medical voice agent capable of real-time clinical transcription and query resolution.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
\vspace{-3pt}
\resumeSubHeadingListStart
    \resumeSubheading
      {Senior Member Technical (AI/ML)}{December 2023 -- July 2025}
      {ADP India Pvt. Ltd.}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Designed and deployed a \textbf{Knowledge-Graph based RAG pipeline} on \textit{AWS Neptune} \& \textit{AWS Bedrock} orchestrated via \textit{LangGraph}, enhancing financial data processing accuracy and minimizing AI hallucinations. Recognized as \textbf{runner-up in the ADP Global Hackathon.}}
        \resumeItem{Developed an intelligent \textbf{Process Mining solution for Global Payroll Services} using \textit{Apache Spark} and \textit{Airflow} to analyze transaction patterns across millions of client records, optimizing payment workflows and eliminating operational bottlenecks across \textbf{73 payroll cycles per client on average}.}
        \resumeItem{Engineered an \textbf{agentic assistant} built on \textit{LangGraph} and \textit{LangChain} that drafts context-aware emails and schedules meetings in real-time by checking live calendars within user chat sessions, saving equivalent to \textbf{24 hours per user per month}; currently rolled out across all ADP employees.}
        \resumeItem{Built a \textbf{scalable QR code detection, decoding, and masking pipeline} using fine-tuned \textit{YOLOv8} for multi-orientation detection and \textit{OpenCV} for automated region masking, sanitising financial documents prior to downstream processing at scale across millions of payroll documents.}
        \resumeItem{Developed an \textbf{Indic PII detection and redaction system} for financial regulatory compliance using fine-tuned NER models via \textit{HuggingFace Transformers} and \textit{SpaCy} with \textit{IndicNLP}, identifying sensitive entities — Aadhaar, PAN, account numbers, names across 10+ Indic scripts — from payroll and HR documents.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
\vspace{-3pt}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Junior Data Scientist}{June 2021 -- December 2023}
      {Claim Genius Pvt. Ltd.}{Remote, India}
      \resumeItemListStart
        \resumeItem{Built a high-performance \textbf{Instance Segmentation pipeline} using \textit{Detectron2} served via \textit{FastAPI} for vehicle parts identification, improving segmentation accuracy to \textbf{95\% mAP} and accelerating assessment throughput by \textbf{26\%}; integrated \textit{GradCAM++} visualisations for regulatory model interpretability, enabling stakeholders to audit spatial reasoning behind predictions.}
        \resumeItem{Engineered an \textbf{automated ML pipeline failure tracing system} using \textit{MLflow} to monitor inference-time distributions and surface root-cause analysis on mispredictions, \textbf{reducing manual diagnosis time by 30\%} and enabling faster corrective action.}
        \resumeItem{Deployed an \textbf{image super-resolution and denoising ensemble} combining \textit{SWIN2SR Transformer} and \textit{NAFNet} pre-trained models to upscale and denoise compressed input images, \textbf{reducing model failures by 16\%} and improving downstream prediction accuracy by \textbf{12\%}.}
        \resumeItem{Improved data pipeline quality by building an \textbf{automatic labelling error-detection service} using \textit{Scikit-learn} confidence scoring that flagged curation errors — \textbf{saving 6 man-hours per head per sprint} — and trained \textit{PyTorch} \textbf{GAN models for synthetic image generation} to resolve class imbalance in rare damage categories.}
        \resumeItem{Extended damage assessment capabilities by designing a \textbf{geometric flat-tyre detection approach} via \textit{OpenCV} polygon analysis of tyre and rim regions — enabling reliable detection with zero curated data — and boosted \textbf{vehicle damage severity classification by 3\% per class} through a fusion ensemble combining \textit{PyTorch} CNN features with \textit{XGBoost} structured metadata.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
    \small
    \item \textbf{Languages \& Query:} Python, SQL, MATLAB, Bash
    \item \textbf{LLM Training \& Inference:} Full fine-tuning, PEFT / LoRA / QLoRA, Instruction Tuning, RLHF / DPO, Mixed-precision (bf16/fp16), Gradient Checkpointing, DeepSpeed / FSDP, Flash Attention, vLLM, TGI, Quantisation (GPTQ / AWQ / bitsandbytes), HuggingFace Transformers, DSPy
    \item \textbf{Agentic \& RAG Systems:} LangChain, LangGraph, GraphRAG, Agentic Pipelines, Tool-use / Function Calling, Multi-agent Orchestration, Retrieval-Augmented Generation
    \item \textbf{Knowledge Graphs \& Vector Search:} Neo4j, AWS Neptune, Pinecone, FAISS, Weaviate, RxNorm API, PubMed API, Knowledge Graph Construction
    \item \textbf{ML \& Deep Learning:} PyTorch, TensorFlow, Scikit-learn, XGBoost, LightGBM, JAX (familiar), Detectron2, YOLO, U-Net, GAN, SWIN Transformer, OpenCV, SpaCy, NLTK
    \item \textbf{MLOps \& Productionisation:} MLflow, Weights \& Biases, Docker, FastAPI, Apache Airflow, Apache Spark, ETL Pipeline Design, Process Mining, CI/CD for ML, Git
    \item \textbf{Cloud \& Infrastructure:} AWS (SageMaker, Bedrock, Neptune, S3, Lambda, EC2), GCP (Vertex AI -- familiar), Azure ML (familiar), Real-time \& Streaming Analytics
    \item \textbf{Data \& Databases:} PostgreSQL, MongoDB, Redis, Big Data Analytics, Statistical Modelling, Experimental Design (A/B Testing)
\end{itemize}

%-----------RESEARCH PROJECTS-----------
\section{Research Projects(TCS Big Data Lab)}
\begin{itemize}[leftmargin=0.15in, label={}]
    \small
    \item \textbf{Multi-label Classification Enhancement} -- Improved multi-label classification by generating synthetic data for rare tail-labels using MLSMOTE + LLSF-DL deep learning hybrid. \textit{Python, MATLAB, TensorFlow, MLSMOTE}
    \item \textbf{Session-based Recommendation with Graph Neural Networks} -- Built a GNN-based recommendation engine that captures graph-structure features to recommend items during active user sessions. \textit{Python, PyTorch, GNN}
\end{itemize}

%-----------CERTIFICATIONS-----------
\section{Certifications}
\begin{itemize}[leftmargin=0.15in, label={}]
    \small
    \item \textbf{Agentic Knowledge Graph Construction} -- DeepLearning.AI $\times$ Neo4j \hfill \textit{Aug 2025}
    \item \textbf{Neo4j Fundamentals} -- Neo4j GraphAcademy \hfill \textit{Jul 2025}
    \item \textbf{Pretraining LLMs} -- DeepLearning.AI $\times$ Upstage \hfill \textit{Feb 2025}
    \item \textbf{TensorFlow Developer Certificate} -- Coursera \hfill \textit{August, 2020}
    \item \textbf{Deep Learning Specialization} -- DeepLearning.AI, Coursera \hfill \textit{April, 2020}

\end{itemize}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {M.Sc. Computer Science (Big Data Analytics)}{}
      {Central University of Rajasthan}{Kishangarh, India}
    \resumeSubheading
      {Integrated B.Sc. B.Ed. (Physical Sciences and Education)}{}
      {Regional Institute of Education (NCERT), Bhubaneswar}{Bhubaneswar, India}
  \resumeSubHeadingListEnd\vspace{-2pt}

\end{document}
